---
title: "NR_5021_project"
authors: "Husain Agha, James Ostlie, Clare Gietzel, Hannah Legatzke"
date: "10/3/2018"
output: html_document
---

#Better Know an R Package
##R/Cowplot
Cowplot is a package developed to work in tandem with R/ggplot2. From the cowplot cran page, "The cowplot package is a simple add-on to ggplot2. It is meant to provide a publication-ready theme for ggplot2, one that requires a minimum amount of fiddling with sizes of axis labels, plot backgrounds, etc."


```{r library, message = FALSE}
library(ggplot2,cowplot)
library(tidyverse)
```

###Load in the data
We are using a data set that is within ggplot2 as well as a dataset collected from class responses.

```{r data}
animal <- msleep

weight <- c(74,63,112,70,55,50,75,59,93,88.64,54.4,84,68.18,130,100,79.54,77,52,79.5,68.2,57.72)

sleep<- c(6,6,6,6.5,6.5,7,7,7,7,7,7,7,7,7,7.25,7.5,7.5,8,8,8,9)

class_sleep <- data_frame(weight,sleep)

class_sleep_summary<- summarize(class_sleep,
                                mean.sleep = mean(sleep),
                                mean.weight = mean(weight))
class_sleep_summary
```

##ggplot2
First we will make several different plots using solely ggplot2 functions

```{r ggplot}

p <- ggplot(animal, aes(x = order, y = sleep_total)) + theme(axis.text.x = element_text(face = "italic", angle = 90, vjust = 0.5)) + geom_point() + aes(colour = log(bodywt))
p 
sleep.plot<-ggplot(msleep, aes(x=msleep$sleep_total, y=msleep$bodywt,colour=order))+geom_point()+labs(x="Mean sleep (hours)", y= "Mean body weight (kg)")
sleep.plot



```
## The cowplot difference
Notice that in cowplot, the default gray background and grid lines present in ggplot2 are missing. This same design can also be achieved in ggplot using "+ theme_classic"

One unique feature of cowplot is the capacity to add images to your plots. For instance, we can add an image of an elephant to the background. To include this feature, we must first download the package "magick." You can change the size of the background image using "scale="
```{r}
#install.packages("magick")
library(magick)
library(ggplot2)
library(cowplot)
elephant<-image_read('https://github.com/Hiagha/NR5021/blob/master/elephant.png?raw=true')
elephant.background<-ggdraw()+draw_image(elephant,scale=0.8)+draw_plot(sleep.plot)
elephant.background
```
## Labeling
You can also use cowplot to add labels to plots. The x and y axis denote where you want the label to appear on the plot.
```{r}
elephant.background+draw_label("Image publically available from pngimg.com", x=0.5, y=0.9, size=12, fontface = "italic")
```

## Comparing plots
Say we wanted to look at the animal sleep data set without the elephant data points, which are the mammals with the two largest masses in the data set. We can create a new data set without this point and plot the Mass vs. Mean Sleep as before

```{r}
no.elephant.animal<-animal[-36,]
#View(no.elephant.animal)
no.elephant.sleep.plot<-ggplot(no.elephant.animal, aes(x=no.elephant.animal$sleep_total, y=no.elephant.animal$bodywt,colour=order))+geom_point()+labs(x="Mean sleep (hours)", y= "Mean body weight (kg)")
no.elephant.sleep.plot
```


